|

### 2025-06-03 manuscript_tf/figures.Rmd
update

(ref:overall) Cumulative COVID-19 cases number for selected European countries since the beginning of the pandemic. Source: COVerAGE-DB [@riffe2021data].
(ref:descriptive) Periods of school closure since the beginning of the COVID-19 pandemic for selected European countries and their reason: regular academic break versus closure due to government decisions. Source: @unesco2022https.
(ref:country) Standardized effect of the smooth term in Generalized Additive Model by country. Standardized effects are reported to compare the shape of the curve between countries.
(ref:age) Standardized effect of the smooth term in Generalized Additive Model by age group. Standardized effects are reported to compare the shape of the curve between age groups.
(ref:te) Matrix of Transfer Entropy coefficients according to every age group combination for each of the selected European country. Age groups on the x-axis are influencing the age groups on the y-axis ($ag\,x \rightarrow\,ag\,y$). The significance of each Transfer Entropy coefficient is provided in Appendix 2.

@@

df_global <- read_csv(here("data/df_global.csv"))
df_global_age <- read_csv(here("data/df_global_age.csv"))
```

>>>>

(ref:overall) Cumulative COVID-19 cases number for selected European countries since the beginning of the pandemic. Source: COVerAGE-DB (Riffe, Acosta, and COVerAGE-DB team 2021).
(ref:descriptive) Periods of school closure since the beginning of the COVID-19 pandemic for selected European countries and their reason: regular academic break versus closure due to government decisions. Source: United Nations Educational, Scientific and
Cultural Organization (UNESCO) (2022).
(ref:country) Standardized effect of the smooth term in Generalized Additive Model by country. Standardized effects are reported to compare the shape of the curve between countries.
(ref:age) Standardized effect of the smooth term in Generalized Additive Model by age group. Standardized effects are reported to compare the shape of the curve between age groups.
(ref:te) Matrix of Transfer Entropy coefficients according to every age group combination for each of the selected European country. Age groups on the x-axis are influencing the age groups on the y-axis ($ag\,x \rightarrow\,ag\,y$). The significance of each Transfer Entropy coefficient is provided in Appendix 2.

@@

# df_global <- read_csv(here("data/df_global.csv"))
# df_global_age <- read_csv(here("data/df_global_age.csv"))
```

### 2025-06-03 manuscript_tf/manuscript_blind.Rmd
update

---
title: |
  Divergent Impacts of COVID-19 School Closures on Youth Infection Dynamics: Evidence from 12 European Countries
author:
  - name: Damien Dupré
    affil: 1
    email: damien.dupre@dcu.ie (corresponding author)
  - name: Edgar Morgenroth
    affil: 1
    email: edgar.morgenroth@dcu.ie
affiliation:
  - num: 1
    address: |
      Dublin City University Business School, Glasnevin, Dublin 9, Ireland
# thanks:
#   author

# author:
#   - name: Author 1
#     affil: 1
#     email: Email 1
#   - name: Author 2
#     affil: 2
#     email: Email 2
# affiliation:
#   - num: 1
#     address: |
#       Affiliation 1
#   - num: 2
#     address: |
#       Affiliation 2

>>>>

---
title: |
  Divergent Impacts of COVID-19 School Closures on Youth Infection Dynamics: Evidence from 12 European Countries
# author:
#   - name: Damien Dupré
#     affil: 1
#     email: damien.dupre@dcu.ie (corresponding author)
#   - name: Edgar Morgenroth
#     affil: 1
#     email: edgar.morgenroth@dcu.ie
# affiliation:
#   - num: 1
#     address: |
#       Dublin City University Business School, Glasnevin, Dublin 9, Ireland
# thanks:
#   author

author:
  - name: Author 1
    affil: 1
    email: Email 1
  - name: Author 2
    affil: 2
    email: Email 2
affiliation:
  - num: 1
    address: |
      Affiliation 1
  - num: 2
    address: |
      Affiliation 2
